Many claims of group polarization are plausibly false due to inappropriate statistics

### 2022-11-20 GroupPolarizationStatmod/paper/ms.tex
expanded t-test table
added quotes from dissertation

% \usepackage{fontspec} 
% \renewcommand{\thesubsection}{\arabic{subsection}.}
% FONTS
% \usepackage[usenames,dvipsnames]{color}
% \usepackage{xunicode}
% \usepackage{xltxtra}
% \defaultfontfeatures{Mapping=tex-text}
% % \setromanfont[Ligatures={Common}, Variant=01]{Hoefler Text}
% % \setromanfont[Ligatures={Common}, Variant=01]{Palatino}
% \setromanfont[Ligatures={Common}, Variant=01]{Baskerville}
% % \setromanfont[Ligatures={Common}, Variant=01]{STIX Two Math}
% % \setmathrm{Baskerville}
% % \setromanfont[Ligatures={Common}, Variant=01]{Plantagenet Cherokee}
% % \setmainfont [BoldFont={STIX Two Text SemiBold}, Ligatures={Common},
% % Numbers={OldStyle}, Variant=01]{STIX Two Math}
% % \setmathrm{STIX Two Math}
% % \setmainfont [BoldFont={STIX Two Text SemiBold}, Ligatures={Common},
% % Numbers={OldStyle}, Variant=01]{STIX Two Text}
% % \setromanfont [Ligatures={Common},
% % Numbers={OldStyle}, Variant=01]{STIX Two Text}
% \setmonofont[Scale=0.95]{PT Sans}

@@

>>>>

@@

\begin{quote}
In our introductory social psychology course, 
we have for many years used the [group polarization experimental paradigm] as
a laboratory exercise. The exercise works beautifully, but one must be
careful to forewarn a class that [group polarization] does not occur with every 
group\ldots and that the effect is not large. 
\par\raggedleft\cite[p. 205]{Brown1986}
\end{quote}

\begin{quote}
One of the most robust findings in social psychology is that of attitude polarization 
following discussion with like-minded others.
\par\raggedleft\cite[p. 267]{Cooper2001}
\end{quote}
